### 2015-03-15 abstract.tex
typo
update abstract

The primary goal of this work is to provide a general framework for what a software development organization
should measure and how to report on those measurements.  The focus is providing a single number
to represnet the entire
organization and not just the development efforts.  That single number is considered the CRI score. The secondary goal of this work is to provide
a framework for storing the necessary data.

>>>>

The primary goal of this work is to provide a general framework for what a software development organization
should measure and how to report on those measurements.  The focus is providing a single number
to represent the entire
organization and not just the development efforts.  That single number is considered the 
Cumulative Result Indicator (CRI) score. The secondary goal of this work is to provide
a framework for storing the necessary data.
